---
title: "Nonnamaker_Exercise7"
output: pdf_document
---

**Question 1:** Write a function that returns the odd (1, 3, 5, etc.) rows of any dataframe passed as an argument.

```{r}
rm(list=ls())
iris <- read_csv("~/Box/personalStuff/School/PhD/biocomputingFall2018/Biocomp-Fall2018-181012-Exercise7/iris.csv")
head(iris)
length(iris$Sepal.Length) # 150
odd <- seq_len(nrow(iris)) %% 2 # get the odd rows
odd
odddata <- data.frame(x=iris[odd==1, ]) # now make a data frame of the odd rows
odddata
```

Brittni: We wanted this in a function, but you have all the right parts. I have written a chunk below transforming your code into a function. (-0.5)
```{r}
returnOdd=function(dataFrame){
  odd <- seq_len(nrow(dataFrame)) %% 2 # get the odd rows
  odddata <- data.frame(x=dataFrame[odd==1, ]) # now make a data frame of the odd rows
  return(odddata)
 }
```

2. Repeat a subset of last week’s exercise, but write functions to accomplish these tasks.

**Question 2:**

***Part 1:*** Return the number of observations for a given species included in the data set

```{r}
head(iris)
str(iris)
# a - return number of observations for a given species in the data set
numspecies <- function(species){
  speciesiwant <- iris[iris$Species==species,]
  obs <- nrow(speciesiwant)
  return(obs)
}
species="setosa" #this is redundant based on how you executed numspecies. "numspecies(species)" would work also.
numspecies(species="setosa")
```

***Part 2:*** Return a dataframe for flowers with Sepal.Width greater than a value specified by the function user
The mean for sepal length is 5.84, so let's do larger than the mean:

```{r}
large <- function(length){
  largesepal <- iris[iris$Sepal.Length>length,]
  return(largesepal)
}
large(5.85)
```  
  
***Part 3:***
Write the data for a given species to a comma-delimited file with the given species name as the file name.

```{r}
str(iris)
writedata <- function(iris,species,workdir) {
  x <-iris[iris$Species==species,]
  write.csv(x, file=paste(workdir,species,".csv", sep=""))
}

writedata(iris,"versicolor",workdir = getwd())
```

***Turning in your assignment via GitHub***
Once you have committed all changes to your local Git repos and pushed all of those commits to the forked repo on GitHub, you can “turn in” your assignment using a pull request. This can be done from the GitHub repo website. When viewing the forked repo, select “Pull requests” in the upper middle of the screen, then click the green “New pull request” button in the upper right. You’ll then see a screen with a history of commits for you and your collaborator, select the green “Create pull request button”. In the text box next to your user icon near the top of the page, remove whatever text is there and add your last name. Then click the green “Create pull request” button.
